Co-citations in context

### 2019-06-12 cocit_r.tex
fixed first para of Results section

We assembled three exemplar datasets using keyword searches for the terms `applied physics', `immunology', and `metabolism' (Materials and Methods).  We used the the WoS extended classification of five major research areas comprising life sciences and biomedicine, physical sciences, social sciences, technology, and arts and humanities and matched our applied physics dataset to physical science, and our immunology and metabolism datasets to the life science and biomedicine research areas respectively. We analyzed the composition of the  references in our three datasets according to the five research areas in the Web of Science for the years 1985, 1995, and 2005. We observed that 84.2\% of the references in the applied physics dataset were classified as belonging to the WoS physical sciences research area and 93.7\% and 92.1\% of the references in the immunology and metabolism datasets respectively belonged to the life sciences and biomedicine research area,  However, corresponding reference content for the WoS superset was 33.4\% (physical sciences) and 52.9\% life sciences and biomedicine. These data suggest at a high level (i) misspecification (ii) strongly that references are likely to belong to the same research area as the publications that cite them rather than being drawn evenly from all five research areas. Our observations are in agreement with \cite{wallace_lariviere_gingras_2012} who found that, often, a majority of an article's citations are from the specialty of the article, although that percentage varied among disciplines in the eight specialties they investigated: from approximately 39\% to 89\% for 2006.

>>>>

We assembled three exemplar datasets using keyword searches for the terms `applied physics', `immunology', and `metabolism' (Materials and Methods).

To study the disciplinary composition of references in our custom datasets, we used the the WoS extended classification consisting of 153 subjects aggregated into the five major research areas of life sciences and biomedicine, physical sciences, social sciences, technology, and arts and humanities. We measured the frequency with which these five major research areas occur in WoS for the years 1985, 1995, and 2005 and observed the following proportions: (i) life sciences and biomedicine (52.9\%), physical sciences (33.4\%), social sciences (7.2\%), technology (17.9\%), and arts and humanities (1\%). We then matched our applied physics dataset to physical science, and our immunology and metabolism datasets to the life science and biomedicine research areas respectively. We analyzed the composition of the references in our three datasets and observed that 84.2\% of the references in the applied physics dataset belonged to physical sciences, and 93.7\% and 92.1\% of the references in the immunology and metabolism datasets respectively belonged to the life sciences and biomedicine research area. These data suggest at a high level (i) that applying a discipline-indifferent model in Monte Carlo simulations would result in misspecification (ii) strongly that references are likely to belong to the same research area as the publications that cite them rather than being drawn evenly from all five research areas. Our observations are in agreement with \cite{wallace_lariviere_gingras_2012} who found that, often, a majority of an article's citations are from the specialty of the article, although that percentage varied among disciplines in the eight specialties they investigated: from approximately 39\% to 89\% for 2006.
